### 2017-01-04 R/tutorial.Rmd
Changes to tutorial and website
Update to tutorial and pomodoros

@@

```{r libs2, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
library("devtools")
install_github(repo = "syounkin/ITHIM")
library("ITHIM")
```

>>>>

## ITHIM Tutorial

### Installing the package

@@

```{r libs2, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
library("devtools")
install_github(repo = "syounkin/ITHIM", ref = devel)
library("ITHIM")
```

### Built-in Example

```{r example, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
example("ITHIM-package")
```

### Step-by-step
